We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-19 outputs/paper/paper.qmd
now Rohan can't say the estimand isn't clearly stated in the intro
more edits

What I am trying to get to here is that I don't actually really mind Jack Antonoff's music, I kind of like it, but I still say his voice with the same tone that everyone else does. There's just something about him... this sense that he's everywhere... and that he's just such a nice guy... Why do music people seem to be a little annoyed with him? What is it about Antonoff music that is so Antonoff-y? Is the Jack Antonoff-fication of pop something we should be worried about?

To find an answer to this question, I turned to statistics, people who know more than me about describing music, and the overlord of engineered virality itself -- the Spotify API. Using a logistic regression model, I was able to determine that Spotify's `danceability` feature was the most important in predicting whether or not a song had any Antonoff involvement. During interview with Glen McDonald, an engineer at Spotify, I learned that the `valence` and `danceability` variables were created by hiring college interns to tag whether or not songs were positive or danceabile. In the discussion section, I armchair a bit about what I think this `danceability` feature, which has so much uncertainty cooked into it, is really capturing: visceral-ness. Which validates everyone's seemingly visceral reaction to new Antonoff releases, and the popularity of his music.

@@

Around the time that Midnights came out, I came across a video on Twitter of a guy, Caleb Gamman, guessing which songs on Midnights were produced by Antonoff within seconds [@citeTweet]. The tweet reads: "im able to instantly detect if jack antonoff worked on a song due to a visceral hatred of his production style". He nails it. Only one song on the album wasn't produced by Antonoff, and he guesses it.

>>>>

What I am trying to get to here is that I don't actually really mind Jack Antonoff's music, I kind of like it, but I still say his voice with the same tone that everyone else does. There's just something about him... this sense that he's everywhere... and that he's just such a nice guy... Why do music people seem to be a little annoyed with him? What is it about Antonoff music that is so Antonoff-y?

To find an answer to this question, I turned to statistics, people who know more than me about describing music (Youtubers), and the overlord of engineered virality itself -- the Spotify API. Can Spotify's audio features dataset help us determine what makes Antonoff music so Antonoff-y?

I spoke to Caleb Gamman, a Youtuber and Antonoff-production-style hater who had a tweet go viral around the time of Taylor Swift's *Midnights* release, in which he predicts whether or not a song was produced by Antonoff within seconds. A real-life logistic regression, if you will. Using an actual logistic regression model, I was able to determine that Spotify's `danceability` feature was the most important in predicting whether or not a song had any Antonoff involvement. During an interview with Glen McDonald, an engineer at Spotify, I learned that the `valence` and `danceability` variables were created by hiring college interns to tag whether or not songs were positive or danceable. In the discussion section, I listen to the songs with the highest danceability scores, and make an argument that this `danceability` feature, which has so much uncertainty cooked into it, is really capturing visceral-ness. We can capture something about Antonoff's music with these variables, and it might just be that subjective "ick" that many people feel and others enjoy that we're all just trying to describe.

@@

Around the time that *Midnights* came out, I came across a video on Twitter of a guy, Caleb Gamman, guessing which songs on Midnights were produced by Antonoff within seconds [@citeTweet]. The tweet reads: "im able to instantly detect if jack antonoff worked on a song due to a visceral hatred of his production style". He nails it. Only one song on the album wasn't produced by Antonoff, and he guesses it.
